---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hw04pdcwilbourne

<!-- badges: start -->
<!-- badges: end -->

hw04pdcwilbourne defines a recursive sequence and allows the user to experiment with it. The user is able to identify future numbers in the sequence given the starting three, and the user is able to plot the outputs of that sequence on a line graph. The package also checks for errors in the inputs to ensure the functions work as intended.

## Installation

This package is only available at the permission of the author at

``` {r}
install.packages("hw04pdcwilbourne")
```

## Example

This is a basic example which shows you how to call calcn, define a dataframe to input to calcn2, and call calcn2 on that dataframe:

```{r example}
library(hw04pdcwilbourne)
# Defines first three numbers in the sequences as 2, 4, and 3, and asks to find the 4th number in the sequence.
calcn(x = c(2, 4, 3), n = 4)

# Defines a data frame containing four columns: the first three numbers in the sequence, and then the number to find in the sequence
my_data <- tibble::tribble(
  ~x, ~y, ~z, ~n,
  2,4,3,3,
  2,4,3,4,
  2,4,3,5,
  2,4,3,6,
  2,4,3,7,
  2,4,3,8,
  2,4,3,9,
  2,4,3,10,
  2,4,3,12)

# Plots the output values generated by the data frame supplied by the user
calcn2(my_data)

```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.
