---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hw04pdcwilbourne

<!-- badges: start -->
<!-- badges: end -->

hw04pdcwilbourne defines a recursive sequence and allows the user to experiment with it. The user is able to identify future numbers in the sequence given the starting three, and the user is able to plot the outputs of the sequence on a line graph. The package also checks for errors in the inputs to ensure the functions work as intended.

## Installation

This package is only available at the permission of the author at

``` {r eval = FALSE}
install.packages("hw04pdcwilbourne")
```

## Example

This is a basic example which shows you how to call rcrsv_solve, define a dataframe to input to rcrsv_plot, and call rcrsv_plot on that dataframe:

```{r example}
library(hw04pdcwilbourne)
# Defines first three numbers in the sequences as 2, 4, and 3, and asks to find the 4th number in the sequence.
rcrsv_solve(x = c(2, 4, 3), n = 4)

# Defines a data frame containing four columns: the first three numbers in the sequence, and then the number to find in the sequence
my_data <- tibble::tribble(
  ~x, ~y, ~z, ~n,
  2,4,3,3,
  2,4,3,4,
  2,4,3,5,
  2,4,3,6,
  2,4,3,7,
  2,4,3,8,
  2,4,3,9,
  2,4,3,10,
  2,4,3,12)

# Plots the output values generated by the data frame supplied by the user
rcrsv_plot(my_data)
```


